Transformer-Based Reranking \\for Improving Korean Morphological Analysis Systems

### 2024-01-12 contents/draft.tex
Pictures added for Authors

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
    {\textbf{Jihee Ryu} received his B.S. degree in computer science \& engineering from Chungnam National University, Daejeon, Rep. of Korea, in 2006. He received his M.S. degree in computer science from KAIST, Daejeon, Rep. of Korea, in 2010. He is currently a Senior Researcher at ETRI, Daejeon, Rep. of Korea. His research interests include natural language processing, deep learning, and knowledge graph completion.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
    {\textbf{Soojong Lim} received his B.S. degree in mathematics from Yonsei University, Seoul, Rep. of Korea, in 1997. He also received his M.S. degree and Ph.D. in computer science from Yonsei University, in 1998 and 2014, respectively. He is currently a Principal Researcher at ETRI, Daejeon, Rep. of Korea. His research interests include natural language processing, deep learning, and large language \& crossmodal models.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
    {\textbf{Oh-Woog Kwon} received his B.S. degree in computer engineering from Kyungpook National University, Rep. of Korea, in 1992, his M.S. degree in computer science from KAIST, Rep. of Korea, in 1995, and his Ph.D. degree in computer engineering from the Pohang University of Science and Technology (POSTECH), Rep. of Korea, in 2001. Since 2004, he has been working with the Language Intelligent Research Section, Electronics and Telecommunications Research Institute (ETRI), Daejeon, Rep. of Korea, where he is currently a Director. His major research interests include natural language processing, large language models, and mathematical reasoning.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
    {\textbf{Seung-Hoon Na} received his Ph.D. degree in computer science from POSTECH in 2008. Currently, he is a Professor at the Dept. of Computer Science at Jeonbuk National University. Previously, he was a Senior Researcher at the Electronics and Telecommunications Research Institute, Rep. of Korea, after working at the School of Computing at Natural University of Singapore. His research interests include natural language processing, information retrieval, and machine learning.}
    \end{biography}

>>>>

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt]{author1}}
    {\textbf{Jihee Ryu} received his B.S. degree in computer science \& engineering from Chungnam National University, Daejeon, Rep. of Korea, in 2006. He received his M.S. degree in computer science from KAIST, Daejeon, Rep. of Korea, in 2010. He is currently a Senior Researcher at ETRI, Daejeon, Rep. of Korea. His research interests include natural language processing, deep learning, and knowledge graph completion.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt]{author2}}
    {\textbf{Soojong Lim} received his B.S. degree in mathematics from Yonsei University, Seoul, Rep. of Korea, in 1997. He also received his M.S. degree and Ph.D. in computer science from Yonsei University, in 1998 and 2014, respectively. He is currently a Principal Researcher at ETRI, Daejeon, Rep. of Korea. His research interests include natural language processing, deep learning, and large language \& crossmodal models.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt]{author3}}
    {\textbf{Oh-Woog Kwon} received his B.S. degree in computer engineering from Kyungpook National University, Rep. of Korea, in 1992, his M.S. degree in computer science from KAIST, Rep. of Korea, in 1995, and his Ph.D. degree in computer engineering from the Pohang University of Science and Technology (POSTECH), Rep. of Korea, in 2001. Since 2004, he has been working with the Language Intelligent Research Section, Electronics and Telecommunications Research Institute (ETRI), Daejeon, Rep. of Korea, where he is currently a Director. His major research interests include natural language processing, large language models, and mathematical reasoning.}
    \end{biography}

    \begin{biography}
    {\includegraphics[width=60pt,height=70pt]{author4}}
    {\textbf{Seung-Hoon Na} received his Ph.D. degree in computer science from POSTECH in 2008. Currently, he is a Professor at the Dept. of Computer Science at Jeonbuk National University. Previously, he was a Senior Researcher at the Electronics and Telecommunications Research Institute, Rep. of Korea, after working at the School of Computing at Natural University of Singapore. His research interests include natural language processing, information retrieval, and machine learning.}
    \end{biography}
